Replication on multicore considering hierarchy and characteristics of the network

### 2013-04-29 paper.tex
Added visualization of broadcast simulation on MST tree.

\stefan{We have an example for this, where the MST is essentially a
  path through the graph}

@@

\stefan{We have experiments showing this}

@@

>>>>

An example is obvious in Figure~\ref{fig:mst_gruyere_operations}. The
level of parallelism is only two. Cores 00 to 15 are dealt with in
parallel to cores 16 to 31. Other than that, there is no further
parallelism although it is possible to ``split up'' communication with
every new ``round'' (i.e.\ send operations of nodes).

@@

We show an example of bad scheduling in
Figure~\ref{fig:mst_gruyere_operations}. When core 08 sends its six
messages, it does so in naive order (here: in increasing node ID
order). This is inefficient, as the latency of the broadcast is
dominated by cores 12, 24 and 28 rather than cores 9, 10 and 11. A
better schedule for sending messages to the children of core 8 would
be to start with the child from which the longest path emerges.

@@

In Figure~\ref{fig:mst_gruyere_operations}, we show the order of
operations for sending a broadcast message along the MST given in
Figure~\ref{fig:mst_gruyere}.

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=.35,transform shape]
    % Insert visualization
    \input{graphs/visu}
  \end{tikzpicture}
  \caption{Visualization of operations for sending a message along the
    tree. Red boxes represent send operations, blue boxes represent
    receive operations and arrows messages sent between cores.}
  \label{fig:mst_gruyere_operations}
\end{figure}
